Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-24 manuscript/manuscript.tex
Modified density-based discretization algorithm in manuscript

Variations in the density function of an arbitrary tesseroid introduces 
a new type of error into the numerical approximation: only a few point 
masses would not reproduce the effect of the density variations.
The modified version of the adaptive discretization algorithm may help 
in reducing this kind of error, but as it only takes into account the 
dimensions of the tesseroid and the distance to the computation point, 
it's not well suited to fully perform this task.

@@

\noindent where the delta ratio $\delta$ is a predefined constant value 
and $L_r^\text{sm}/L_r$ is a tesseroid size ratio, where 
$L_r^\text{sm}$ and $L_r$ are the radial dimensions of the tesseroid 
that is currently analysed and of the \emph{original} one, 
respectively.
On the first iteration, the former tesseroid corresponds to the 
\emph{original} one, so $L_r^\text{sm} = L_r$, but for future 
iterations this radial dimension will be computed as the difference of 
the top and bottom radii of the subdividing tesseroid.
The tesseroid size ratio is intended to reduce the number of probable 
unneeded discretizations and focus on discretizations that will 
significantly reduce the numerical error.
A big subdividing tesseroid with small maximum absolute difference would 
introduce more numerical error than a small subdividing tesseroid with 
higher maximum absolute difference.

@@

It's easy to see that the delta ratio indirectly controls how many 
times the tesseroids will be subdivided based on the variation of the 
density function.
Therefore it determines the accuracy involving the numerical error that 
the density variation introduces and also the computation time: a lower 
value of $\delta$ will produce more discretizations leading to an 
increase in the accuracy of the approximation but also in the 
computation time.
This raises the need to determine a maximum value of $\delta$ that 
ensures an acceptable accuracy while minimising the computation time. 
We will perform this determination with the same methodology as the one 
applied to the $D$ ratio: compare the numerical model with the 
analytical solutions for a spherical shell.

>>>>

Variations in the density function of an arbitrary tesseroid introduce 
a new type of error into the numerical approximation: only a few point 
masses would not reproduce the effect of the density variations.
The modified version of the adaptive discretization algorithm may help 
in reducing this kind of error, but as it only takes into account the 
dimensions of the tesseroid and the distance to the computation point, 
it's not well suited to fully perform this task.

@@

\noindent where the delta ratio $\delta$ is a predefined constant value 
and $L_r^\text{sm}/L_r$ is a tesseroid size ratio, where 
$L_r^\text{sm}$ and $L_r$ are the radial dimensions of the tesseroid 
that is currently analysed and of the \emph{original} one, 
respectively.
On the first iteration, the former tesseroid corresponds to the 
\emph{original} one, so $L_r^\text{sm}/L_r$ is equal to one, but for 
future iterations this radial dimension will be computed as the 
difference of the top and bottom radii of the subdividing tesseroid.
The tesseroid size ratio is intended to reduce the number of probable 
unneeded discretizations and focus on discretizations that will 
significantly reduce the numerical error.
A big subdividing tesseroid with small maximum absolute difference would 
introduce more numerical error than a small subdividing tesseroid with 
higher maximum absolute difference.

@@

It's easy to see that the delta ratio indirectly controls how many 
times the tesseroids will be subdivided based on the variation of the 
density function.
Therefore it determines the accuracy involving the numerical error that 
the density variation introduces and also the computation time: a lower 
value of $\delta$ will produce more discretizations leading to an 
increase in the accuracy of the approximation but also in the 
computation time.
This raises the need to determine a maximum value of $\delta$ that 
ensures an acceptable accuracy while minimising the computation time.
